```{r imports}
library(ggplot2)
library(dplyr)
```

```{r MCC}
data.mcc = read.csv("mcc-data.csv")
ggplot(data.mcc, aes(x=100*Iteration, y=Success.Mean, colour=factor(Nu),
                     ymin=Success.Mean-Success.Std, ymax=Success.Mean+Success.Std)) +
  geom_line() +
  geom_errorbar(width=20) +
  scale_y_continuous() +
  labs(title="MCC with Focus Tracker (r=0.15)",
       x="Iteration", y="Success (Testing Set)", colour="Nu")
```

First coord of thetaFile is p, second coord is the sigma
Expect Gaussian kernel to work better with good hyperparam
j
$$p \in [1,5]$$
$$l \in [2,3]$$

Linear kernel imposes strong correlation between different data points
=> initially very fast learning because high correlations
However, with proper settings of hyperparams Gauss kernel better fits true distr of data

Mu trades off accuracy and computational complexity

```{r GP}
data = read.csv("gp-data.csv")
str(data)

ggplot(data, aes(x=100*Iteration, y=Success.Mean, colour=factor(Kernel))) +
  geom_line() +
  scale_y_continuous() +
  labs(title="GP with Focus Tracker (r=0.15)",
       x="Iterations", y="Average Success (Testing Set)", colour="Kernel")
```

```{r GP-gauss}
data = read.csv("gp-gauss-data.csv")
str(data)

ggplot(data, aes(x=100*Iteration, y=Success.Mean, colour=factor(Kernel))) +
  geom_line() +
  scale_y_continuous() +
  labs(title="GP with Focus Tracker (r=0.15)",
       x="Iterations", y="Average Success (Testing Set)", colour="Kernel")
```

```{r all}
data = read.csv("results-all-tidy.csv", na.strings = "--")
#data <- data[11:nrow(data),] # drop really good performing linear kernel
str(data)

best.mcc = data.mcc[data.mcc$Nu == 0.01,]

ggplot(
  rbind(
    data.frame("Kernel"="MCC (Nu=0.01)", best.mcc[,c("Iteration", "Success.Mean", "Success.Std")]),
    data %>%
      filter(Kernel %in% c(
        "Linear (sigma=5)",
        "Gaussian (p=4;l=2)",
        "Gaussian (p=3;l=2)"
      )) %>%
      group_by(Kernel, Iteration) %>%
      summarize(Success.Mean = Success.Mean[1], Success.Std = Success.Std[1])
  ),
  aes(x=100*Iteration, y=Success.Mean, colour=Kernel,
      ymin=Success.Mean-Success.Std, ymax=Success.Mean+Success.Std)) +
  scale_y_continuous() +
  geom_line() +
  geom_point() +
  geom_errorbar(width=20) +
  labs(title="GP with Focus Tracker (r=0.15)",
       x="Iteration", y="Success (Testing Set)", colour="")
```
